A practical look at genetic algorithms

### 2015-12-06 evolutionaryComputation/practicals/report.tex
added pargraph about mutation

\paragraph{Mate selection} MateSelection implements tournament select.
This is the only mate selection algorithm implemented currently.

\paragraph{Member factories} The member factories are able to create
members from strings. These are either the tightly linked or randomly
linked. Then the tightly or randomly linked
functions can also be wrapped in a mutation function,
which will mutate the string before passing it to the factory.
Its an decorator idea, only with functions.

>>>>

\paragraph{Mate selection} MateSelection implements tournament select.
This is the only mate selection algorithm implemented.

\paragraph{Member factories} The member factories are able to create
members from strings. These are either the tightly linked or randomly
linked. 
\subparagraph{Mutation} Then the tightly or randomly linked
functions can also be wrapped in a mutation function,
which will mutate the string before passing it to the factory.
Its an decorator idea, only with functions.
